Chemical potential of liquids and mixtures via Adaptive Resolution Simulation

### 2014-05-20 writeDown/pub.jcp/resubmission.tex
revise...

(1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).

@@

\recheck{do not say that...}
Finally, the referee asked us to ``{\it ameliorate} the language; we are fully aware of not being mother tongue Oxford academics, but we asked several colleagues to read the paper and tell us if it was understandable; we got only positive comments, we cannot do more than that.

@@

(1) Thermodynamic limit for the \recheck{atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}

@@

The method is mathematically rigorous and for some aspects even
exact. Conditions (1) and (2) are ideal, so it was important to know
how they can be met in \recheck{practical simulations, especially in
the mixture systems that the solute concentration is dilute.} The aim of this paper is: {\bf to
  explore the numerical accuracy of the theory (for the chemical
  potential) proposed in Ref.5}.  We have done it for thirteen
representative and computationally expensive systems.  We hope the
referee can recognize that this effort is a non-trivial one. However
as asked by him/her, we have added all the simulations requested (see
below).

@@

% \recheck{
%   The main purpose of the paper was to show the numerical accuracy of the theory, so we did not provide the theoretical derivation of
% }
% We have taken such a comment as a motivation to make an effort and finalize a derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
We have taken such a comment as a motivation to \recheck{provide the} derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.

@@

\recheck{The Fig.2 (Fig.4 in the revision) plots the density profile only for the HYB region, as the caption states.}
% We disagree.
\recheck{The relatively large deviation is due to the sampling error, because the
  number of TBA molecules in the system is very small (80, see the Table II, i.e.~the Table IV in the revision).
  We could reach a much better accuracy of the density if we do longer simulations,
  but it would require much more computer time.}
% We could reach a much higher accuracy if we set the level
% of accuracy of the thermodynamic force higher (but requires more
% computer time).
However, we wanted to show that even with 20 percent of
(maximum) difference we get the chemical potential accurate and the
density in the AT region flat.

>>>>

(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.
% (1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).

@@

Finally, the referee asked us to {\it ameliorate} the language; we are fully aware of not being mother tongue Oxford academics, but we asked several colleagues to read the paper and tell us if it was understandable; we got only positive comments, we cannot do more than that.

@@

(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.

@@

The method is mathematically rigorous and for some aspects even
exact. Conditions (1) and (2) are ideal, so it was important to know
how they can be met in {practical simulations, especially in
the mixture systems that the solute concentration is dilute.} The aim of this paper is: {\bf to
  explore the numerical accuracy of the theory (for the chemical
  potential) proposed in Ref.5}.  We have done it for thirteen
representative and computationally expensive systems.  We hope the
referee can recognize that this effort is a non-trivial one. However
as asked by him/her, we have added all the simulations requested (see
below).

@@

% \recheck{
%   The main purpose of the paper was to show the numerical accuracy of the theory, so we did not provide the theoretical derivation of
% }
% We have taken such a comment as a motivation to make an effort and finalize a derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
We have taken such a comment as a motivation to {provide the} derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
Although developed before the submission of this paper, this result was not presented, because the paper was intended to investigate only the numerical accuracy.

@@

{The Fig.2 (Fig.4 in the revision) plots the density profile only for the HYB region, as the caption states.}
% We disagree.
{The relatively large deviation is due to the sampling error, because the
  number of TBA molecules in the system is very small (80 for mole-fraction 0.02, see the Table II, i.e.~the Table IV in the revision).
  We could reach a much better accuracy of the density if we do longer simulations,
  but it would require much more computer time.}
% We could reach a much higher accuracy if we set the level
% of accuracy of the thermodynamic force higher (but requires more
% computer time).
However, we wanted to show that even with 20 percent of
(maximum) difference we get the chemical potential accurate and the
density in the AT region flat.
